---
title: "UCSB Xaringan Demonstration"
subtitle: "Showcase how to use UCSB theme"
author: "Nathaniel Grimes"
institute: 
  - "Bren School of Environmental Science & Management"
  - "University of California at Santa Barbara"
date: "6/13/2021"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: ["ucsb.css","uwm-fonts"]
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: "16:9"
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE, htmltools.preserve.raw = FALSE)
```

# Xaringan presentation

## What is Xaringan?

- [`Xaringan`](https://github.com/yihui/xaringan) is an R package that can be used to create slides

- The name comes from Sharingan from the anime Naruto! `r emoji::emoji("laugh")`

- How to install:

```{r eval=FALSE, include=TRUE}
devtools::install_github('yihui/xaringan')
```

- How to get started:

    - [Xaringan github](https://github.com/yihui/xaringan)

---
# Xaringan presentation

- Here are some great tutorials:

  - [Xaringan github](https://github.com/yihui/xaringan)

  - [Yihui's tutorial](https://slides.yihui.org/xaringan/#1)
  
  - [Making Slides in the Tada!-verse](https://apreshill.github.io/data-vis-labs-2018/slides/06-slides_xaringan.html#1)
  
  - [Making slides in R Markdown](http://arm.rbind.io/slides/xaringan.html#1)

- Some useful extensions for `Xaringan`

  - [`xaringanExtra` R package](https://github.com/gadenbuie/xaringanExtra)
  
  - [`xaringanthemer` R packge](https://pkg.garrickadenbuie.com/xaringanthemer/index.html)
  
  - [Xaringan Gallery](https://xaringan.gallery/)
  
  - [`DT` R package for interactive tables](https://rstudio.github.io/DT/)


---
# UCSB theme

- How to enable the UCSB theme: Need to replace placeholders

```md
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: ["XXX", "fonts"]
```

- The UCSB theme for `Xaringan` presentation is suitable to work with a 16:9 aspect ratio

```md
nature:
  highlightStyle: github
  highlightLines: true
  countIncrementalSlides: false
  ratio: "16:9"
```

---
# UCSB themes theme

- We can make `blockquotes` by calling `<uc-blockquote>some texts</uc-blockquote>`

<uc-blockquote>This is a blocked quote</uc-blockquote> 

- Highlight text using `**text**` like **this**

- Italic text using `*text*` like *this*

- Bold text using `.bold[text]` like .bold[text]

---
# UCSB theme

- We can change the color of any text by using `.color[text]`. I included all the colors from the UCSB brand team for quick ready access

  - [UCSB palette](https://brand.ucsb.edu/visual-identity/color#digital): `blue[text]`,`.grey[text]`,`.gold[text]`,...fill out the rest
  - .blue[UCSB Navy], .grey[Grey accent], .seagreen[Seagreen], .mist[Mist], .clay[Clay], .sandstone[sandstone]



---
class: bold-last-item

# UCSB theme

- add `class: bold-last-item` at the beginning of each slide to switch on the **Bold-Last-Item**  Still doesn't work

```css
---
class: bold-last-item
```
--
- For example
--
- Bullet list 1
--
- Bullet list 2
--
- Bullet list 3
---
class: highlight-last-item

# UCSB theme
- add `class: highlight-last-item` at the beginning of each slide to switch on the **Highlight-Last-Item**
--
- For example
--
- Bullet list 1
--
- Bullet list 2
--
- Bullet list 3
---
```{r xaringan-extra-styles, echo=FALSE}
xaringanExtra::use_extra_styles(
  hover_code_line = TRUE,         #<<
  mute_unhighlighted_code = TRUE  #<<
)
```
# R code and plot output

```{r, fig.height=4.5, fig.width=9, fig.retina=2, fig.align='center', message=FALSE, warning=FALSE}
library("tidyverse")
cars %>% 
  ggplot(aes(x = dist, y = speed)) + 
  geom_point() + 
  geom_smooth(method = 'lm', formula = y ~ poly(x, 2)) + 
  theme_bw(base_size = 24) 
```


---

class: title-slide-section-blue

# Change the color palette with a new section

### Sub set font

- How does the text look

- Use **bold**

---

class: title-slide-section-gold

# Test first level

### Test second level

---
class: title-slide-final

# Final Slide

usethis::use_github_pages(branch = "main")<button class="xaringanextra-clipboard-button" type="button" aria-label="Copy code to clipboard" style="color: rgb(0, 0, 0);"><i class="fa fa-clipboard"></i> Copy Code</button>
