---
title: "UCSB Xaringan with Scribble"
subtitle: "Useful drawing tool"
author: "Nathaniel Grimes"
institute: 
  - "Bren School of Environmental Science & Management"
  - "University of California at Santa Barbara"
date: "6/13/2021"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: ["ucsb.css","chocolate-fonts"]
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: "16:9"
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE, htmltools.preserve.raw = FALSE)

knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```


```{r xaringan, echo=FALSE}
xaringanExtra::use_xaringan_extra(c("scribble"))
```

```{css echo = FALSE}
.xe-scribble__tools.minimized {
  display: none;
}
```

# Scribble is a cool tool to write on top of slides

## Add it through `xaringanExtra::use_scribble()` at the beginning of your slides

Click `S` to open and engage scribble!

---

# Blank slide to draw to your heart's content

---

# Base scribble includes a pencil icon in the top right for all slides. I prefer to mask the icon so it isn't distracting

```css
.xe-scribble__tools.minimized {
  display: none;
}
```

- Include that chunk after loading in scribble to hide the pencil icon

- Otherwise you can have `use_scribble()` and click on the pencil to engage drawing mode

---

# Limitations

- In large presentations with lots of slides and features, scribble appears to slow down the slide transition time

- Have to save slides as pdf to keep drawings otherwise they always disapper

- Check out more options at [Garrick Aden-Buie's github](https://github.com/gadenbuie/xaringanExtra)